\phantomsection
\cleardoublepage
\addcontentsline{toc}{section}{\literature}
\begin{thebibliography}{MMM99}

\bibitem[LOR87]{bib:marching-cubes}
  {\bf William E. Lorensen, Harvey E. Cline}\\
  {\em Marching Cubes: A high resolution 3D surface construction algorithm.}\\
  In: Computer Graphics, Vol. 21, Nr. 4, 1987.

\bibitem[CRA09]{gig2009}
  {\bf Cyril Crassin, Fabrice Neyret, Sylvain Lefebvre, Elmar Eisemann}\\
  {\em GigaVoxels: Ray-Guided Streaming for Efficient and Detailed Voxel
  Rendering.}\\
  ACM SIGGRAPH Symposium on Interactive 3D Graphics and Games (I3D), 2009.

\bibitem[CRA08]{gig2008}
  {\bf Cyril Crassin, Fabrice Neyret, Sylvain Lefebvre}\\
  {\em Interactive GigaVoxels Technical Report}\\
  INRIA Technical Report, 2008.

\bibitem[GOB08]{other}
  {\bf Enrico Gobbetti, Fabio Marton, Jose Antonio Iglesias Guitian}\\
  {\em A single-pass GPU ray casting framework for interactive out-of-core
  rendering of massive volumetric datasets.}\\
  The Visual Computer: International Journal of Computer Graphics, 2008.

\bibitem[KRÜ03]{raycast}
  {\bf Jens Krüger ir Rüdiger Westermann}\\
  {\em Acceleration Techniques for GPU-based Volume Rendering.}\\
  Computer Graphics and Visualization Group, Technical University Munich, 2003.

\bibitem[RAY99]{gradients}
  {\bf Harvey Ray, Hanspeter Pﬁster, Deborah Silver, Todd A. Cook}\\
  {\em Ray Casting Architectures for Volume Visualization.}\\
  MITSUBISHI ELECTRIC RESEARCH LABORATORIES, 1999.

\bibitem[DRE88]{transfer}
  {\bf Robert A. Drebin, Loren Carpenter ir Pat Hanrahan}\\
  {\em Volume Rendering.}\\
  Computer Graphics, Volume 22, Number 4, August 1988.

\bibitem[LEV87]{first}
  {\bf Marc Levoy}\\
  {\em Display of Surfaces from Volume Data.}\\
  Computer Science Department University of North Carolina Chapel Hill, NC 27514. 1987

\end{thebibliography}
